Modeling Liver with Glisson's Capsule in Real-Time Medical Simulations

### 2013-05-31 Doc/Vrst2013/vrst2013.tex
ADD: reformulation in 4. chapter
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@583 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

\numberofauthors{4}
\author{
% 1st. author
\alignauthor
Tom\'a\v{s} Golembiovsk\'y\\
       \affaddr{Faculty of Informatics}\\
       \affaddr{Masaryk University}\\
       \affaddr{Brno, Czech Republic}\\
       \email{nyoxi@ics.muni.cz}
% 2nd. author
\alignauthor
Igor Peterl\'ik\\
       \affaddr{Institut Hospitalo-Universitaire}\\
       \affaddr{Strasbourg, France}\\
       \email{Igor.Peterlik@ihu-strasbourg.eu} % TODO
% 3rd. author
\alignauthor
Christian Duriez\\
       \affaddr{INRIA}\\
       \affaddr{Lille, France}\\
       \email{Christian.Duriez@inria.fr} % TODO
\and
% 4th. author
\alignauthor
Stephan\'e Cotin\\
       \affaddr{INRIA}\\
       \affaddr{Lille, France}\\
       \email{Stephane.Cotin@inria.fr} % TODO
}

@@

Moreover, we are able to reproduce
the measurements presented in~\cite{Hollenstein2006,Nava2008} with less than 1\% error.
We do not model the time-dependent behaviour though.
In this simulation we prescribe the the internal pressure of 30\,kPa. The other
parameters of the model were obtained like this: First we fix the stiffness of
parenchyma to $E_p$=30\,kPa to match the scenerio without capsule. Then,
assuming the thickness $t$=93\,$\mu$m of the capsule (reported as average in
the paper) we run several simulations with different capsule stiffness $E_c$.
We have found the lowest error is when $E_c$=3\,MPa. All the stiffness
parameters lie within the ranges measured in the paper.

>>>>

\numberofauthors{4}
\author{
% 1st. author
\alignauthor
Tom\'a\v{s} Golembiovsk\'y\\
       \affaddr{Faculty of Informatics}\\
       \affaddr{Masaryk University}\\
       \affaddr{Brno, Czech Republic}\\
       \email{nyoxi@ics.muni.cz}
% 2nd. author
\alignauthor
Igor Peterl\'ik\\
       \affaddr{Institut Hospitalo-Universitaire}\\
       \affaddr{Strasbourg, France}\\
       \email{Igor.Peterlik@ihu-strasbourg.eu} % TODO
% 3rd. author
\alignauthor
Christian Duriez\\
       \affaddr{INRIA}\\
       \affaddr{Lille, France}\\
       \email{Christian.Duriez@inria.fr} % TODO
\and
% 4th. author
\alignauthor
St\'ephane Cotin\\
       \affaddr{INRIA}\\
       \affaddr{Lille, France}\\
       \email{Stephane.Cotin@inria.fr} % TODO
}

@@

In the second step, we use our simulation to reproduce the displacements values measured experimentally in~\cite{Hollenstein2006,Nava2008}.
Since the Young's moduli of neither parenchyma ($E_p$) nor capsule ($E_c$ were specified, we obtained both as follows: first, 
performed a set of simulations without the capsule for different values of ($E_p$): the value that provided a good match 
with reported displacement after applying the negative pressure of 30\,kPa inside the tube was $E_p$=30\,kPa. 
The, we fixed the thickness of the capsule as $T$=93\,$\mu$m (reported as an average in the paper) and 
using $E_p$=30\,kPa, we performed repeatedly the simulation with the capsule using different values of the Young's modulus
of the capsule in order to minimize the displacement error. The minimal error (under 1\%) was obtained 
for Young's modulus $E_c$=3\,MPa which lies in the range of capsule elasticity reported by experimental measurements.

%Moreover, we are able to reproduce
%the measurements presented in~\cite{Hollenstein2006,Nava2008} with less than 1\% error.
%We do not model the time-dependent behaviour though.
%In this simulation we prescribe the the internal pressure of 30\,kPa. The other
%parameters of the model were obtained like this: First we fix the stiffness of
%parenchyma to $E_p$=30\,kPa to match the scenerio without capsule. Then,
%assuming the thickness $t$=93\,$\mu$m of the capsule (reported as average in
%the paper) we run several simulations with different capsule stiffness $E_c$.
%We have found the lowest error is when $E_c$=3\,MPa. All the stiffness
%parameters lie within the ranges measured in the paper.
